Hydras \& Co.

### 2023-11-17 doc/chapter-primrec.tex
Fix a latex error
Corrections to chapter 11 (primitive recursive functions)

\input{movies/snippets/primRecExamples/SuccIsPR}

@@

\index{ackermann}{Exercises}
\begin{exercise}

Prove the following lemmas (which may help to solve the next  exercise).

@@

\textbf{Note:}  The function \texttt{boundedSearch} is defined
in Library \href{../theories/html/hydras.Ackermann.primRec.html}{Ackermann.primRec}. 
\end{exercise}

\begin{exercise}
Prove that the function which returns the  integer square root of any natural number  is primitive recursive.

@@

>>>>

\input{movies/snippets/PrimRecExamples/SuccIsPR}

@@

\index{ackermann}{Exercises}
\begin{exercise}[The integer square root]

\mbox{}
\vspace{4pt}

\noindent
 \textbf{1)} 
Please consider the following specification of the function \texttt{boundedSearch} defined in 
\href{../theories/html/hydras.Ackermann.primRec.html}{Ackermann.primRec}.

\inputsnippets{isqrt/boundedSearchSpec}

Prove the following lemmas.

@@

\noindent
\textbf{2)} 
Let us consider the following definition of the relation `` $r$ is the integer square root of $n$ ''.

\inputsnippets{isqrt/isqrtSpec}

Prove that the function which returns the  integer square root of any natural number  is primitive recursive (you may use 
the function \texttt{boundedSearch} for this purpose).

@@

With respect to proof methods, we will see a first \emph{proof by induction on the set of all primitive recursive functions}.
First, we will prove a property shared by all primitive function, 
then show that the Ackermann function doesn't satisfy this property.
